Considering scale in multilayer animal social networks

### 2020-06-15 paper/manuscript.Rmd
remind qs

# Discussion

>>>>

# Discussion
<!-- 1)
First, to what degree does the social scale of relationships, spatial
scale of landscapes, and temporal scale of analysis influence our ability to
interpret complex social systems? 
-->

<!-- 2)
Second, can variation in the social, spatial,
and temporal scale improve predictions associated with biological differences in
seasonal resource availability and social association?

+
We conclude with
perspectives for further development and application of scale in multilayer
networks with respect to phenotypes and individual fitness,
movement ecology and collective movement, and habitat selection
and space use.
-->
